---
title: "Alcohol vs Seat choice"
author: "Tracy Alset"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot



```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The "back" max value is higher than both "front" and "middle". But in general the alcohol levels for the "back" are higher than both "front" and " middle".

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

Based on the numerical values it seemed like more people sit in the "middle" part than both "front" and "back", and then "front" then "back". and the alcohol levels for the "back" (based on the mean) show that they are the highest at these seats, and then the "middle" and then the "front".

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The low P value doesn't help us here. so we use the tukeyhsd test.

```{r}
plot(TukeyHSD(model1))
```

The high negative value of the difference between front and back shows that the mean value for the back is very much higher than the one for the front. for middle-back the difference is a little smaller but it's still relatively high so the mean value of the middle is lower than the one for the back. but for the middle-front the difference is almost negligable ( the subtraction value is close to zero ) so the middle's and the front's means are almost similar.


## Conclusions




based on all of the data collected, it seems that the alcohol levels for the people sitting in the back are higher than the middle and the front. in addition to that, based on the TukeyHSD test it seemed that the mean values for the middle and the front are close to each other. In this project we saw how the p value test didn't really help us so we had to use the TukeyHSD test.

