---
title: "Alcohol vs Seat choice"
author: "Tracy Alset"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot



```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The "back" max value is higher than both "front" and "middle". But in general the alcohol levels for the "back" are higher than both "front" and " middle".

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

Based on the numerical values it seemed like more people sit in the "middle" part than both "front" and "back", and then "front" then "back". and the alcohol levels for the "back" (based on the mean) show that they are the highest at these seats, and then the "middle" and then the "front".

## Inferential Tests

## Conclusions


